---
title: "데이터 임상의학 w/ R (2)"
date: Aug 11, 2018
author: "Yoon-Ho Hong, MD, PhD"
output:
  html_document:
    toc: yes
    toc_float: true
---

## R & Rstudio 설치하기  
The R Project for Statistical Computing https://www.r-project.org/  
An integrated development environment (IDE) for R https://www.rstudio.com/

## rstudio.cloud (alpha)
Rstudio server cloud https://rstudio.cloud/  


## Getting Help  
?mean  
??"weighted mean"

## Using Packages   
install.packages("dplyr")  
library(dplyr)  

## Working directory
getwd()  
setwd()

## Vectors  

Creating vectors  
```{r}
c(2, 4, 6)  
2:6  
seq(2, 10, by=0.5)  
rep(1:3, times=3)
rep(1:3, each=3)
```
<br>

Vector functions
```{r}
x <- c(10:20, 1, 3, 10, 12) # variable assignment 
sort(x)
sort(x, decreasing = TRUE) # argument 
rev(x)
length(x)
range(x)
unique(x) # see unique values
table(x) # see vounts of values
```
<br>

Selecting vector elements (by position)
```{r}
a = c("apple", "banana", "melon", "grape")
a[4]
a[-4]
a[2:4]
a[-(2:4)]
a[c(1,3)]
```
<br>

Selecting vector elements (by value)
```{r}
x[x == 10]
x[x < 10]
x[x %in% c(1, 2, 5)]
```

## Programming   
for loop 
```{r}
# summation 1 to 10
j = 0
for (i in 1:10){
  j = i + j
}
j
```
<br>

while loop
```{r}
i = 0; j = 0
while (i < 10){
  i = i + 1
  j = j + i
}
i; j
```
<br>

if... else statements 
```{r}
if (i > 3){
  print("i larger than 3")
} else {
  print("i less than 3")
}
```
<br>

functions 
```{r}
square = function(x){
  squared = x*x
  return(squared)
}
square(4)
```

## Math functions 
```{r}
sum(x)
mean(x)
median(x)
max(x)
min(x)
sd(x)
var(x)
quantile(x)
round(1.8734, 2)
exp(x)
log(x)
x^2
```

## Environment
```{r}
ls()
rm(i)
```

## R objects

When you create a `variable` you reserve some space in memory. The variables are assigned with R `objects`. There are many types of R objects which includes... 

- vector
- list
- matrix
- data frame
- factor

Data types of atomic vectors includes...

- numeric
- logical (boolean)
- character

## Data type conversion 
```{r}
tc = c(0,1,1,0);class(tc)  
tc.logic = as.logical(tc)
tc.num = as.numeric(tc.logic)
tc.char1 = as.character(tc.num)
tc.char2 = as.character(tc.logic)
```

## Matrix 
```{r}
# create a matrix from x
mat = matrix(x, ncol = 3)
# select rows/columns/elements
mat[1,]
mat[,3]
mat[3,2]
t(mat) # transpose 
mat %*% t(mat) # matrix multiplication
```

## List
```{r}
lst <- list(x = 1:5, y = c('a', 'b'))
lst[[2]]
lst$y
lst[2]
lst["y"]
```

## Data frames
```{r}
df <- data.frame(n = 1:3, s = c('a', 'b', 'c'))
df[1,]
df[3,2]
str(df)
dim(df)
nrow(df);ncol(df)
```

## Factor 
```{r}
char = c("a", "b", "c", "b", "c", "d")
fac = factor(char)
levels(fac)
```

## 데이터 불러오기

Read a comma separated value (csv) file
```{r}
demograph = read.csv("Demographic.csv")
head(demograph)
```
<br>

Read a delimited text file  
```{r}
proact = read.delim("proact_sample.txt", sep="|") 
# random 1/20 sample of the PROACT dataset
```

## 데이터 쓰기

```{r}
demograph$Age = round(demograph$Age)
write.csv(demograph, file = "demograph_roundage.csv", row.names = F, quote = F)
write.table(demograph, file = "demograph_roundage.txt", quote = F, row.names = F)
```

## 그래프 

Scatter plot  
```{r}
attach(mtcars)
plot(wt, mpg, pch=19)
pairs(mtcars)
pairs(mtcars[c("disp", "hp", "wt", "qsec")])
```
<br>

Histogram
```{r}
hist(mtcars$mpg)
hist(mtcars$mpg, freq = F)
lines(density(mtcars$mpg))
plot(density(mtcars$mpg))
```
<br>

Bar Plot 
```{r}
counts <- table(mtcars$gear)
barplot(counts, main="Car Distribution", 
  	xlab="Number of Gears")
```
<br>

Grouped Bar Plot
```{r}
counts <- table(mtcars$am, mtcars$gear)
barplot(counts)
barplot(counts, col=c("blue","red"),
 	legend = rownames(counts))
barplot(counts, col=c("blue","red"),
 	legend = rownames(counts), beside=TRUE)
```

Boxplot  
```{r}
boxplot(mpg~cyl,data=mtcars, main="Car Milage Data", 
  	xlab="Number of Cylinders", ylab="Miles Per Gallon")
```


Saving graph  
: Export -> Save As...
: You can also save the graph via code using one of the following functions...

- pdf("mygraph.pdf")	
- png("mygraph.png")
- jpeg("mygraph.jpg")	
- bmp("mygraph.bmp")
- postscript("mygraph.ps")	 

## 연습 문제

Slack #textbook 채널에 가서 ISLR pdf 파일을 열어 Chapter 2, Page 54-57 의 연습문제 8-10 을 풀어보자. 

https://rstudio.cloud 에 가서 sign up 한후, 아래 link 에 접속하여, https://rstudio.cloud/spaces/2905/join?access_code=QuMv1uIYqUTizsyRrXX8JjK8eoRpk5vJO%2BoiiqgZ
Data medicine 101 스페이스의 Basics 프로젝트를 copy 한 후 R script 를 작성한다. 




